\layerOne{Weekly Reports}
\setcounter{section}{14}
\layerTwo{2015}
\setcounter{subsection}{36}

\layerThree{7 Sep 2015 - 11 Sep 2015}
\begin{itemize}
\item Made browser tabs closeable
\item Init Requirements and Specifications in LaTeX
\item Added Panic button to GUI
\item Image loading: XML file now derived from IMG file name and path instead of storing
that information in the IMG file.
\item Division of BigIntegers fixed, Multiplication of negative Integers fixed
\end{itemize}

\layerThree{14 Sep 2015 - 18 Sep 2015}
\begin{itemize}
\item Tested and documented some git features.
\item Produced conflicts in git: Managed to resolve them finally. It was challenging. Further
testing required.
\item Tried to install safari. Waiting for Help desk...
\item Made the browser work again. Several fixes: Removed layouter, changed locking mechanism,
set to native browser
\end{itemize}

\layerThree{21 Sep 2015 - 25 Sep 2015}
Used XMF to do exercises with meta-classes \begin{itemize} 
\item to understand the concept of class, object, instantiation and inheritance
\item to override the default meta-object-protocol, be redefining new/get/set etc.
\item to understand the default behaviour of XMF
\end{itemize}

\layerThree{28 Sep 2015 - 2 Oct 2015}
\begin{itemize} 
\item Continued experiments with meta-classes
\item Gathered ideas for website; some experiments with html.
\end{itemize}

\layerThree{5 Oct 2015 - 9 Oct 2015}
\begin{itemize} 
\item Preparation for discussions about intrinsics.
\item Fr: Travel
\end{itemize}

\layerThree{12 Oct 2015 - 16 Oct 2015}
\begin{itemize} 
\item Mo,Tu,Fr: holiday
\item Making documentation for sceanarios for changes on intrinsic attributes
\item Tiny bugfix in FormsClient
\end{itemize}

\layerThree{19 Oct 2015 - 23 Oct 2015}
\begin{itemize} 
\item Mo: Travel
\item Added Monospace (with anti-alias) font to editor window.
\end{itemize}

\layerThree{26 Oct 2015 - 30 Oct 2015}
\begin{itemize} 
\item Started to fix HTML generation
\end{itemize}

\layerThree{2 Nov 2015 - 6 Nov 2015}
\begin{itemize} 
\item Fixed Live Documentation
\item Drew diagram for intrinsics to verify current model
\end{itemize}

\layerThree{9 Nov 2015 - 13 Nov 2015}
\begin{itemize} 
\item fix syntax highlighting
\item fix \%20 at welcome page
\end{itemize}

\layerThree{16 Nov 2015 - 20 Nov 2015}
\begin{itemize} 
\item fix fonts, test change fonts dynamically
\item fix autocomplete . , ()
\item remove debug noDocFound, isLikelyToBeHTML
\end{itemize}

\layerThree{23 Nov 2015 - 27 Nov 2015}
\begin{itemize} 
\item Diagrams: added InstLevel to associations
\item fixed zoom
\end{itemize}

\layerThree{30 Nov 2015 - 3 Dec 2015}
\begin{itemize} 
\item Modified appearance of associations, added arrows
\item Added boxes for intrinsic Level
\item Multiplicity shows always
\end{itemize}

\layerThree{9 Dec 2015 - 10 Dec 2015}
\begin{itemize} 
\item Visit in Essen
\end{itemize}

\layerThree{14 Dec 2015 - 18 Dec 2015}
\begin{itemize} 
\item Changed label's and arrow's position on associations in diagrams
\item Tried to make DEL-key work in diagrams
\end{itemize}

\layerThree{ToDo}
\begin{itemize}
\item improve webpage
\item Specify FormClient, fix only
\item git commands in Eclipse
\item (nextWeek) MeMo language requirements
\item pw protected folder: \url{https://wincent.com/wiki/git_repository_access_control}
\item Snippets
\item look at/play with Kernel (Object/Class/Attribute)
%\item Use Notepad++ with syntax highlighting for user defined languages: \url{http://weblogs.asp.net/jongalloway/creating-a-user-defined-language-in-notepad}
\item HTMLViewer.xmf: Are ".o", ".xip", ".xto", ".xtd", ".xtml" still in use?
Welcome.xmf: requestURL ...
requirements
\item welcome page does not work in linux
\item experiment: call java function
%\item fix documentation bug (over lunch)
\item rectangular edges only on some edge types
\item Show/hide in Diagram
\item show warning in diagram when drawing nonsense
\item supporting multiple languages
\end{itemize}
